%-------------------------
% Resume in Latex
% Template Author : Shubhi Rani
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{ragged2e}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-3pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSkill}{\item\small\textbf{}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSkillsListStart}{\setlength\multicolsep{0pt}\begin{multicols}{3}\begin{itemize}[leftmargin=*,nolistsep]}
\newcommand{\resumeSkillsListEnd}{\end{itemize}\end{multicols}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Matt Kouba}} & Email : \href{mailto:matt.kouba@gmail.com}{matt.kouba@gmail.com}\\
  \href{https://github.com/mckouba}{Github: https://github.com/mckouba} & 715-292-2190 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Michigan Technological University}{Houghton, MI}
      {BS Computer Engineering;  GPA: 3.40}{May 2023}
	\resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSkillsListStart
	\resumeSkill C/C++/C\#
	% MATLAB
    \resumeSkill Java
    \resumeSkill SharePoint
    \resumeSkill Embedded C/Assembly
    %\resumeSkill MIPS/NIOS Assembly
    \resumeSkill Verilog
    %\resumeSkill Unix
    \resumeSkill Altium Designer 
    \resumeSkill Microsoft Office
    \resumeSkill Power Query/BI
    \resumeSkill Microcontrollers
\resumeSkillsListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {General Motors}{Warren, MI}
    {SW IRT }{May 2022  -  August 2022}
    \resumeItemListStart
        %\item Ensure vehicle features at certain software levels are implemented according to design specifications.
        \item Gather and analyze CAN data between modules to identify causes of DTCs and communication problems between ECUs inside the vehicle.
        %\item Update ECUs present in vehicles to new software levels thorough the development process and if any fail, gather CAN data to determine why and escalate through proper channels if needed.
        \item Created web tool to automate collection of different vehicle build process start dates, reducing time spent by ~90\%, to present at weekly meetings.
        \item Created Power BI and macros to ingest Excel data weekly, reducing time spent by 50\%, to then be presented at weekly staff meetings to show vehicle build progress.
      \resumeItemListEnd
    \resumeSubheading
		{General Motors}{Warren, MI}
        {SW Tools Engineer }{May 2021  -  August 2021}
		\resumeItemListStart
        \item Wrote application to migrate vehicle development plans from Excel to a web-based application so that data could be accessed easier and could be analyzed in the future.
        \item Wrote application to process more than 650 Excel files uploaded to a Sharepoint site including being able to identify duplicate uploads, updated forms, malformed forms, and incomplete forms for collecting semiconductor data.
        %\item Wrote application to interface with Sharepoint to update, verify, and add new part numbers to track their semiconductor tracking completeness.
		\resumeItemListEnd 
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
%still need to add descriptions
\section{Academic Projects}
\resumeSubHeadingListStart
\resumeSubItem{Automotive Ethernet Learning Modules}{Created from the ground up a standalone node that implements Automotive Ethernet and CAN communication protocols.  This can be used along with an Arduino to communicate with another module using the Automotive Ethernet communication protocol. This involved designing a schematic, layout of a PCB, assembly of the PCB, and software design both embedded on the shield and on the Arduino. Advisor: Dr. Aurenice Oliveira}
\resumeSubItem{Streaming Video from a Drone Over the Cellular Network}{Created high level idea of how to transport video from a drone to a user over the cellular network as opposed to using a dedicated radio frequency.  I dealt with the Linux Kernel drivers for the cellular modem, the creation of the video streaming pipeline, and the microprocessor choice.  This used a Nvidia Jetson Nano and a cellular modem connected on a custom made carrier board which was not designed by me.}
\resumeSubItem{CAN FD Arduino Shield}{Created a standalone single channel CAN FD Arduino Shield.  This involved a schematic capture where parts had to be chosen to work with an Arduino and be in stock.  This also involved designing and assembling a PCB and writing software to actually use this shield with an Arduino. Advisor: Dr. Aurenice Oliveira } 
%These will be used in EE5365 to teach students about the CAN FD communication protocol.
\resumeSubHeadingListEnd

%-----------Leadership---------------
\section{Leadership}
\resumeSubHeadingListStart
\resumeSubheading
{Tier 2 Shop Technician}{Houghton, MI}
{Michigan Technological University}{March 2022 - Present}
\resumeSubheading
{President}{Houghton, MI}
{Alpine Ski Team}{April 2022 - Present}
\resumeSubheading
{Vice President}{Houghton, MI}
{Alpine Ski Team}{May 2021 - April 2022}
\resumeSubHeadingListEnd

%-----------Interests-----------------
\section{Interests}
\resumeSkillsListStart
\resumeSkill Mountain Biking 
\resumeSkill Ski Racing
\resumeSkill Programming
\resumeSkill Computers
\resumeSkill Athletics
\resumeSkill Automotive
\resumeSkill Automation
\resumeSkill Embedded Devices
\resumeSkillsListEnd
%-------------------------------------------
\end{document}